Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-03 tex/sections/apm.tex
Fix typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Prover Machine gets as its primary input a vector $(\mathbf{C}_H,\mathbf{C}_P,\mathbf{C}_R)$, where
$\mathbf{C}_H$ is a commitment to the AscEE Heap, $\mathbf{C}_P$ is a commitment to the AscEE Program Area and
$\mathbf{C}_R$ is a commitment to an ordered list of requests. The APM then outputs a final
$\mathbf{accept}$ flag which indicates if the execution has ended successfully and also outputs the updated
commitments to the AscEE Heap and Program Area: $(\mathbf{C}_{H'},\mathbf{C}_{P'},\mathbf{accept})$.

Producing the required outputs from these inputs is not computationally feasible so the APM accepts an auxiliary
input vector $(H,\pi_H,P,\pi_P,R,\pi_R,h)$, where $\pi_X$ is a proof that proves $X$ can be opened w.r.t
$\mathbf{C}_X$. The auxiliary input $h$ is a hint that helps the APM make nondeterministic choices correctly.

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for the NEU and PRU. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example it verifies the signatures of authenticated messages or
    verifies that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept$ flag. More formally it evaluates $(H',accept)=P(H,
    R_{good})$, where $H'$ is the updated heap chunks and the $accept$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and the $accept$ flag is set
    to false if a request execution completes normally.
    \item \textbf{Postprocessor:} This module is responsible for calculating the updated commitments
    $(\mathbf{C}_{H'}, \mathbf{C}_{P'})$ and the final $\mathbf{accept}$ flag. Installing new applications or
    updating the code of existing application is performed by this module.
\end{itemize}

>>>>

The Argennon Prover Machine gets as its primary input a vector $(\mathbf{C}_H,\mathbf{C}_P,\mathbf{C}_R)$, where
$\mathbf{C}_H$ is a commitment to the AscEE Heap, $\mathbf{C}_P$ is a commitment to the AscEE program area and
$\mathbf{C}_R$ is a commitment to an ordered list of requests. The APM then outputs the updated
commitments to the AscEE heap and program area and a final $\mathbf{accept}$ flag which indicates if the execution has
ended successfully or not: $(\mathbf{C}_{H'},\mathbf{C}_{P'},\mathbf{accept})$.

Producing the required outputs from these inputs is not computationally feasible so the APM receives an auxiliary
input vector $(H,\pi_H,P,\pi_P,R,\pi_R,h)$, where $\pi_X$ is a proof that proves $X$ can be opened w.r.t
$\mathbf{C}_X$ and $h$ is a hint that helps the APM make nondeterministic choices correctly.

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for other modules. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example it verifies the signatures of authenticated messages or
    verifies that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept$ flag. More formally it evaluates $(H',accept)=P(H,
    R_{good})$, where $H'$ is the updated heap chunks and the $accept$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and the $accept$ flag is set
    to false if a request execution completes normally.
    \item \textbf{Postprocessor:} This module is responsible for calculating the updated commitments
    $(\mathbf{C}_{H'}, \mathbf{C}_{P'})$ and the final $\mathbf{accept}$ flag. Installing new applications or
    updating the code of existing application is performed by this module.
\end{itemize}

### 2022-09-03 tex/sections/avm.tex
Fix typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Smart Contract Execution Environment (AscEE) is an abstract execution environment for executing Argennon
smarts contracts (a.k.a\ Argennon applications) in a secure and isolated environment. An Argennon application
essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Application Representation (ASAR).

An Argennon Standard Application Representation (ASAR) is a programming language for describing Argennon
applications, optimized
for the architecture and properties of the Argennon platform. This text based representation should be low level
enough to enable easy compilation from any high level programming language and should be high level enough to preserve
the high level information of the application logic and facilitate platform specific compiler optimization at a host
machine. In this regard, the ASAR can be considered as an Intermediate Representation (IR).

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill \emph{external} HTTP requests\footnote{External requests are requests that are not made by other Argennon
applications.}, produce their HTTP responses and update related heap chunks. The execution of requests can be
considered sequential\footnote{Actually requests may be executed in parallel but by performing data dependency analysis
the result is guaranteed to be identical with the sequential execution of requests.} and each request has a separate
\emph{Execution Session}. Therefore, an Execution Session is a separate session of executing application's code in
order to fulfill an External HTTP request. We call this external request the \emph{initiator} of the Execution Session.

The state of an Execution Session will be
destroyed at the end of the session and only the state of heap chunks is preserved. If a session fails and does not
complete normally, it will not have any effects on any heap chunks.

During an Execution Session an application can make \emph{internal} HTTP requests to other applications. Those
requests will not start a new Execution Session and will be executed within the current session. In AscEE making an
HTTP request to an application is similar to a function invocation, and for that reason, we also refer to them as
application calls.

@@

Every Argennon application has two types of memory: local memory and heap. Local memory is not persistent and is
destroyed when the application call ends. Local memory is used for storing local variables and is not directly
addressable. Heap, on the other hand, is persistent and can be used for persisting data between application calls.
Heap is addressable and provides low level direct access. Both local memory and heap are limited, but the
AscEE does not specify any particular limits for them. When an application tries to use too much memory, that may
cause the execution session to end abruptly. In that case, the Execution Session will not have any effects on the
state of the heap.

@@

When an application allocates a new heap chunk, the identifier of the new chunk is not generated by
the AscEE. Instead, the application can choose an identifier itself, provided it has a correct format. This
is an important feature of the AscEE heap which allows applications to use the AscEE heap as a map
data structure\footnote{also called a dictionary.}.
Since the \texttt{chunkID} is a prefix code, any application has its own identifier space, and an application
can easily find unique identifiers for its chunks.

During an Execution Session every heap chunk has an access type which may disallow certain operations. This access
type is declared by the initiator request of the Execution Session:

\begin{itemize}
    \item \texttt{check\_only}: only allows check operations. These operations query the persistence
    status of a memory location.
    \item \texttt{read\_only}: only allows read and check operations.
    \item \texttt{writable}: allows reading and writing.
    \item \texttt{additive}: only allows additive operations. By additive we mean an addition-like operator without
    overflow checking which is associative and commutative. Note that the content of these access blocks cannot be read.
\end{itemize}

@@

At the start of executing requests of a block, a validator can consider two values for every
heap chunk, the size: \texttt{chunkSize} and a size upper bound: \texttt{sizeUpperBound}. The value of
\texttt{chunkSize} can be determined uniquely at the start of
every Execution Session, and it may be updated during the session by the owner application. On the other hand,
the value of \texttt{sizeUpperBound} proposed by the block proposer for each block and is calculated based on values
declared by requests (i.e.\ transactions) declaring chunk resizing. This value needs to be an upper bound of all the
declared values and indicates the upper bound of \texttt{chunkSize} during the execution of requests of a block.

The value of \texttt{chunkSize}, can be modified during an Execution Session. However, the new size values can only be
increasing or decreasing. More precisely, if a request declares that it wants to expand (shrink) a chunk, it can only
increase (decrease) the value of \texttt{chunkSize} and any specified value during the execution
session, needs to be greater (smaller) than the previous value of the chunk's size. Any request that wants to expand
(shrink) a chunk needs to specify a max size (min size). The value of \texttt{chunkSize} can not be set higher
(lower) than this value.

The value of \texttt{chunkSize} at the end of an Execution Session will determine if a memory location at an
offset is persistent or not: Offsets lower than the chunk size are persistent, and higher offsets are not.
Non-persistent locations will be re-initialized with zero at the start of every Execution Session.

Usually an application should not have any assumption about the content of memory locations that are outside the chunk.
While these locations are zero initialized at the start of every Execution Session, it should be noted that multiple
invocations of an application may occur in a single Execution Session, and if one of them modifies a location outside
the chunk, the changes can be seen by next invocations.

There is no way for an application to query \texttt{sizeUpperBound}. As a result, for an application,
accessing offsets higher than \texttt{chunkSize} results in undefined behaviour, while the behaviour is well-defined
in the view of validators.
This enables validators to determine the validity of an offset at the start of the block validation in a parallelized
preprocessing phase without actually executing requests.

@@

The AscEE uses \emph{Authenticated Message Passing} for authorizing operations. In this method, every Execution
Session has a set of authenticated messages, and those messages are \textbf{explicitly} passed in requests to
applications for authorizing operations. These messages act exactly like digital signatures and applications can
ensure that they are issued by their claimed issuer accounts. The only difference is that the process of
message authentication is performed by the AscEE internally and an application does not explicitly verify cryptographic
signatures.

Each Execution Session has a list of authenticated messages. Each authenticated message has an index which will be
used for passing the message to an application as a request parameter. The AscEE uses cryptographic signatures to
authenticate messages for user accounts. The signatures are validated in parallel during the
preprocessing step of the block validation, and any type of cryptographic signature scheme can be used.

>>>>

The Argennon Smart Contract Execution Environment (AscEE) is an abstract high level execution environment for executing
Argennon smarts contracts (a.k.a\ Argennon applications) in a secure and isolated environment. An Argennon application
essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Application Representation (ASAR).

An Argennon Standard Application Representation is a programming language for describing Argennon
applications, optimized
for the architecture and properties of the Argennon platform. This text based representation should be low level
enough to enable easy compilation from any high level programming language and should be high level enough to preserve
the high level information of the application logic and facilitate platform specific compiler optimization at a host
machine. In this regard, the ASAR can be considered as an Intermediate Representation (IR).

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill \emph{external} HTTP requests\footnote{External requests are requests that are not made by other Argennon
applications.}, produce their HTTP responses and update related heap chunks. The execution of requests can be
considered sequential\footnote{Actually requests may be executed in parallel but by performing data dependency analysis
the result is guaranteed to be identical with the sequential execution of requests.} and each request has a separate
\emph{execution session}. Therefore, an execution session is a separate session of executing application's code in
order to fulfill an external HTTP request. We call this external request the \emph{initiator} of the execution session.

The state of an execution session will be
destroyed at the end of the session and only the state of heap chunks is preserved. If a session fails and does not
complete normally, it will not have any effects on any heap chunks.

During an execution session an application can make \emph{internal} HTTP requests to other applications. Those
requests will not start a new execution session and will be executed within the current session. In AscEE making an
internal HTTP request to an application is similar to a function invocation, and for that reason, we also refer to
them as \emph{application calls}.

@@

Every Argennon application has two types of memory: local memory and heap. Local memory is not persistent and is
destroyed when the application call ends. Local memory is used for storing local variables and is not directly
addressable. Heap, on the other hand, is persistent and can be used for persisting data between application calls.
Heap is addressable and provides low level direct access. Both local memory and heap are limited, but the
AscEE does not specify any particular limits for them. When an application tries to use too much memory, that may
cause the execution session to end abruptly. In that case, the execution session will not have any effects on the
state of the heap.

@@

When an application allocates a new heap chunk, the identifier of the new chunk is not generated by
the AscEE. Instead, the application can choose an identifier itself, provided the new id has a correct format. This
is an important feature of the AscEE heap which allows applications to use the AscEE heap as a map
data structure\footnote{also called a dictionary.}.
Since the \texttt{chunkID} is a prefix code, any application has its own identifier space, and an application
can easily find unique identifiers for its chunks.

During an execution session every heap chunk has an access type which may disallow certain operations. This access
type is declared by the initiator request of the execution session:

\begin{itemize}
    \item \texttt{check\_only}: only allows check operations. These operations query the persistence
    status of a memory location.
    \item \texttt{read\_only}: only allows read and check operations.
    \item \texttt{writable}: allows reading and writing.
    \item \texttt{additive}: only allows additive operations. By additive we mean an addition-like operator without
    overflow checking which is associative and commutative. Note that the content of these chunks cannot be read.
\end{itemize}

@@

At the start of executing requests of a block, a validator can consider two values for every
heap chunk, its size: \texttt{chunkSize} and a size upper bound: \texttt{sizeUpperBound}. The value of
\texttt{chunkSize} can be determined uniquely at the start of
every execution session, and it may be updated during the session by the owner application. On the other hand,
the value of \texttt{sizeUpperBound} is proposed by the block proposer for each block and is calculated based on values
declared by external requests (i.e.\ transactions) which want to perform chunk resizing. This value needs to be
an upper bound of all the declared resizing values and indicates the upper bound of \texttt{chunkSize} during the
execution of a block.

The value of \texttt{chunkSize}, can be modified during an execution session. However, the new values of size can
only be increasing or decreasing. More precisely, if a request declares that it wants to expand (shrink) a chunk, it
can only increase (decrease) the value of \texttt{chunkSize} and any specified value during the execution
session, needs to be greater (smaller) than the previous value of the chunk's size. Any request that wants to expand
(shrink) a chunk needs to specify a max size (min size). The value of \texttt{chunkSize} can not be set higher
(lower) than this value.

The value of \texttt{chunkSize} at the end of an execution session will determine if a memory location at an
offset is persistent or not: Offsets lower than the chunk size are persistent, and higher offsets are not.
Non-persistent locations will be re-initialized with zero at the start of every execution session.

Usually an application should not have any assumption about the content of memory locations that are outside the chunk.
While these locations are zero initialized at the start of every execution session, multiple
invocations of an application may occur in a single execution session, and if one of them modifies a location outside
the chunk, the changes can be seen by next invocations.

There is no way for an application to query \texttt{sizeUpperBound}. As a result, for an application
accessing offsets higher than \texttt{chunkSize} results in undefined behaviour, while the behaviour is well-defined
in the view of validators.
This enables validators to determine the validity of an offset at the start of the block validation in a parallelized
preprocessing phase without actually executing requests.

@@

The AscEE uses \emph{Authenticated Message Passing} for authorizing operations. In this method, every execution
session has a set of authenticated messages, and those messages are \textbf{explicitly} passed in requests to
applications for authorizing operations. These messages act exactly like digital signatures and applications can
ensure that they are issued by their claimed issuer accounts. The only difference is that the process of
message authentication is performed by the AscEE internally and an application does not explicitly verify cryptographic
signatures.

Each execution session has a list of authenticated messages. Each authenticated message has an index which will be
used for passing the message to an application as a request parameter. The AscEE uses cryptographic signatures to
authenticate messages for user accounts. The signatures are validated in parallel during the
preprocessing step, and any type of cryptographic signature scheme can be used.

### 2022-09-03 tex/sections/elements.tex
Fix typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Completing an Execution Session requires computational resources. The amount of resources used by an Execution Session
should be monitored and managed, otherwise a malicious user would be able to easily spam and exhaust resources of the
execution environment.

@@

The AscEE has two types of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and \textbf{default} pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). The block proposer decides the
type of the Execution Session for each transaction.

@@

When a transaction fails due to the violation of a limit for a nondeterministic resource, the proposer is
required to exactly specify the application call which violates that limit in the Execution Session. When validators are
executing a monitored session, for each application call, they enforce considerably larger limits for
nondeterministic resources. Only in case the proposer has declared that an application call violates a limit, the
validators will enforce the actual value of the limit. This simple mechanism ensures that, with a very high
probability, validators agree with the proposer, although their measurements could be different.

>>>>

Completing an execution session requires computational resources. The amount of resources used by an execution session
should be monitored and managed, otherwise a malicious user would be able to easily spam and exhaust resources of the
execution environment.

@@

The AscEE has two types of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and \textbf{default} pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). The block proposer decides the
type of the execution session for each transaction.

@@

When a transaction fails due to the violation of a limit for a nondeterministic resource, the proposer is
required to exactly specify the application call which violates that limit in the execution session. When validators are
executing a monitored session, for each application call, they enforce considerably larger limits for
nondeterministic resources. Only in case the proposer has declared that an application call violates a limit, the
validators will enforce the actual value of the limit. This simple mechanism ensures that, with a very high
probability, validators agree with the proposer, although their measurements could be different.

### 2022-09-03 tex/sections/intro.tex
Fix typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

In addition to the ASAR, on the blockchain an Argennon application is stored in the Argennon Prover Machine (APM) code.
This code is used by validators for CI proof verification. The Argennon Prover Machine is a virtual
machine tailored for efficient verification of AscEE computations by
argument systems. The APM has a minimal RISC architecture with a very compact instruction set. This ensures that
its transition function has an efficient circuit complexity.

>>>>

In addition to the ASAR, an Argennon application is stored on the blockchain in the Argennon Prover Machine (APM) code.
This code is used by validators for CI proof verifications. The Argennon Prover Machine is a virtual
machine tailored for efficient verification of AscEE computations by
argument systems. The APM has a minimal RISC architecture with a very compact instruction set. This ensures that
its transition function has an efficient circuit complexity.
